Latent Predicate Networks: Concept Learning with Probabilistic Context-Sensitive Grammars

### 2014-10-21 drafts/cfp/draft.tex
Draft changes.

\title{Latent Predicate Networks: Concept Learning with Probabilistic Context-Sensitive Grammars}
\author{Eyal Dechter,  Josh Rule, Josh Tenenbaum}
\date{}

@@

Finally, inducing probabilistic context-sensitive grammars with latent
predicates threatens to be intractable: our goal is to find a
middle ground between expressivity and tractability. Using tools like
PRISM -- a probabilistic logic programming system that naturally
implements efficient dynamic programming algorithms for our models --
we are able to explore which domains and which grammar architectures
are a good fit for this grammar-based approach.

@@

\subsection{Architecture}

An LPN is an PRCG with 1 unary predicate $S$, and $K$ densely
connected binary predicates ${A_k}_{k=1}^K$ (Figure
\ref{fig:architecture}). Specifically, for each latent predicate
$A_k$, we define rules such that $A_k(w_a,w_b)$ is true for each
possible pair of terminals, $w_a,w_b \in T$. We also define rules such
that $A_k(XY,UV)$ is true for each possible pair of predicates,
$A_i,A_j$, and every possible ordering of the variables $X,Y,U$ and
$V$ across $A_i$ and $A_j$. Finally, we define $S(XY)$ to be the
concatenation of the two arguments of $A_1(X,Y)$.

@@

\section{Implementation}

>>>>

\title{Latent Predicate Networks: Concept Learning with Probabilistic Context-Sensitive Grammars}
\author{Eyal Dechter, Josh Rule, Josh Tenenbaum ADD AFFILIATION}
\date{}

@@

Finally, inducing probabilistic context-sensitive grammars with latent
predicates threatens to be intractable: our goal is to find a
middle ground between expressivity and tractability. Using
PRISM~\cite{DBLP:journals/jair/SatoK01} -- a probabilistic logic programming system that naturally
implements efficient dynamic programming algorithms for our models --
we are able to explore which domains and which grammar architectures
are a good fit for this grammar-based approach.

@@

\subsection{Generic Architecture}

An LPN is an PRCG with 1 unary predicate $S$, and $K$ densely
connected binary predicates $\{A_k\}_{k=1}^K$ (Figure
\ref{fig:architecture}). Specifically, for each latent predicate
$A_k$, we define rules such that $A_k(w_a,w_b)$ is true for each
possible pair of terminals, $w_a,w_b \in T$. $T$ may include the empty
string, but we do not allow latent predicates of the form
$A_k(\epsilon, \epsilon)$: see Section~\ref{sec:implementation}. We also define rules such that $A_k(XY,UV)$
is true for each possible pair of predicates, $A_i,A_j$, and every
possible ordering of the variables $X,Y,U$ and $V$ across $A_i$ and
$A_j$. Finally, we define $S(XY)$ to be the concatenation of the two
arguments of $A_1(X,Y)$.

@@

\section{Implementation \label{sec:implementation}}
